Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

>>>>

Finding the $\contained_{R_{k-2}}(h^*)$ sets of all $h^* \in H^*$ is an instance of the find-all-sorted version of Problem $\mathscr{E}$ (with $H^*$ and $R_{k-2}$ as the input). The cost is $O(n \log n + \out)$ according statement (1) of Lemma~\ref{lmm:hv:type1:cross-r*} and the discussion in Section~\ref{sec:bricks}. Note that, for each $\contained_{R_{k-2}}(h^*)$ computed, the rectangles $r$ therein have been sorted in descending order of $\xright(r)$.
